Results MSRC latent class analysis

### 2021-11-10 manuscript/manuscript.Rmd
Change figure based on reviewer comment

p_res_prob <- ggplot(df_plot, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + facet_wrap(~Variable, nrow = 4, scales = "free") + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
ggsave("p_res_prob.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
p_res_prob
```

>>>>

df_plot$Class <- ordered(df_plot$Class, levels = c("1", "2"), labels = c("Higher-Risk History", "Lower-Risk History"))
df_attempt <- df_plot[df_plot$Variable == "Will likely attempt", ]
df_plot <- df_plot[!df_plot$Variable == "Will likely attempt", ]
p_res_prob <- ggplot(df_plot, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + facet_wrap(~Variable, nrow = 4, scales = "free") + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
ggsave("p_res_prob.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
p_res_prob
```

```{r figpresprob2, include = TRUE, fig.cap="Results of the two-class latent class model for future attempts. Proportion of responses by response category and latent class."}
p_res_prob2 <- ggplot(df_attempt, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
ggsave("p_res_prob2.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
p_res_prob2
```
